The Applications of Model-driven Software Development, A Systematic Literature Review

### 2015-03-24 rmtw/a5/latex8.tex
rev a5

The search terms used can be found in Appendix A. The main search terms are related to MDSD, but related terms such as Model Driven Engineering and code generation were also included.

The inclusion criteria were defined as follows: \newline
\begin{itemize} 
\item Studies including examples about the application of MDSD in industry
\item Studies carried out using a qualitative methodology
\end{itemize}

The exclusion criteria were defined as follows: \newline
\begin{itemize}
\item Informal papers (no defined research questions, no methodology)
\item Non-peer reviewed papers (books, white papers etc.)
\item Studies carried out using a quantitative methodology
\end{itemize}

>>>>

The search keywords used can be found in Appendix A. The main search keywords are related to MDSD, but related keywords such as Model Driven Engineering and code generation were also included.
\newline

The inclusion criteria were defined as follows: 
\begin{itemize} 
\item Studies including examples about the application of MDSD in industry
\item Studies carried out using a qualitative methodology
\end{itemize}

The reason only qualitative studies are included is that they are most appropriate for answering our research questions. This is also supported by Petticrew and Roberts who state that qualitative studies are well-suited for assessing whether a new technology is useful for the type of systems they have to build \cite{petticrew2008systematic}.  
\newline

The exclusion criteria were defined as follows: 
\begin{itemize}
\item Informal papers (no defined research questions, no methodology)
\item Non-peer reviewed papers (books, white papers etc.)
\item Studies carried out using a quantitative methodology
\end{itemize}
